### 2009-03-05 doc/ws-programming-tutorial/doc/tex_appendix/appendix.tex
Finished the Secure Echo Web Service and made first correction of the chapters.

\section{More tutorials}

Other tutorials are:\\
\\
%Oxana reported the status of OGF tutorials:
\begin{itemize}
 \item first tutorial will be given by Oxana and will deal with how to add the 
resources to Nordugrid, .... (will be related mostly to production ARC)
 \item second tutorial will be given by Gabor and he will show the 
interoperability of ARC (video demo will be shown). A-REX - Unicore 
interoperability.
 \item there will be also a tutorial related to ETICS system where the 
possibility of ETICS system to submit a job to ARC and Unicore will be 
presented. The ETICS team has not contacted so far.
\end{itemize}

\section{Important XSD files}

Link to current XSD files.

\task{Provide a list of modules to be loaded! Along with the implemented functionality which can be addressed with XML elements!!}
    mcctcp\\
\begin{verbatim}
<tcp:Listen>
	<tcp:Port>60000</tcp:Port>
	<tcp:Version>4</tcp:Version>
</tcp:Listen>
\end{verbatim}
    mcctls\\
\begin{verbatim}
 			<KeyPath>./clientKey.pem</KeyPath>
			<CertificatePath>./clientCert.pem</CertificatePath>
			<CACertificatePath>./clientCA.pem</CACertificatePath><!-- CACertificatesDir Should be /etc/... blub mention that-->

\end{verbatim}

    mcchttp\\
\begin{verbatim}
                      <next id="soap">POST</next>
                      <next id="plexer">GET</next>
                      <next id="plexer">PUT</next>
\end{verbatim}
    mccsoap\\
\begin{verbatim}
	???<ClientSSLConfig FromFile='filename'/>  
\end{verbatim}

>>>>

\section{Useful tutorials and documentations}

In order to learn more about ARC several other tutorials and documentations have been written:
\begin{itemize}
 \item ARC Web Services Quick Usage Guide~\cite{2008_UNKNOWN}
 \item The Hosting Environment of the Advanced Resource Connector middleware~\cite{2008_Cameron}.
 \item Security framework of ARC1~\cite{QIANG_2008}.
 \item Documentation of the ARC storage system~\cite{Nagy_2008}.

\end{itemize}

\section{Important XSD files}\label{sec:impXSD}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:mcc.xsd,
	caption={[XML schema of configuration files.]\textbf{XML schema of configuration files.}}
	]{../../../src/hed/libs/loader/mcc.xsd}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:tcp.xsd,
	caption={[XML schema of the TCP component.]\textbf{XML schema of the TCP component.}}
	]{../../../src/hed/mcc/tcp/tcp.xsd}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:tls.xssd,
	caption={[XML schema of the TLS component.]\textbf{XML schema of  the TLS component.}}
	]{../../../src/hed/mcc/tls/tls.xsd}

\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:http_xsd,
	caption={[XML schema of the HTTP component.]\textbf{XML schema of the HTTP component.}}
	]{../../../src/hed/mcc/http/http.xsd}

% 
% Questions:
% \begin{itemize}
%  \item The images of the HED structure always are ordered like: TCP - TLS - HTTP - PLEXER - SOAP - Web Service   but the source code examples are: TCP - TLS - HTTP - SOAP - PLEXER - Web Service\\
% --- ANSWER BY WEIZHONG: In my understanding (because plexer is not my initial idea), plexer (as a sort of hub) can be put at both after http or soap. If you put after soap,then you are doing switching for different web services. While I put it after http, because somehow, I need to switch the message after http-processing, in more detail, one branch for soap and then web service/s,
%  one branch for a non-soap service/server (the SP Service is not a service based on SOAP, actually it is based on http, so it is kind of web application).
% 
% \item The HED does not act as a front end server which delegates its task to new instances acting on a diffrent port such that the daemon is always available. 
% \end{itemize}

% 
% 
 \task{RENAMING HED configuration file into~ARC service configuration file - proposed by Marek}
 \task{(echo service) client configuration file - proposed by Marek}
 \task{Check commas using \url{http://leo.stcloudstate.edu/punct/comma.html}}

 \task{Bisher noch nicht beachtet: \\
\\\textcolor{urgent}{
In general, a comma is used when the
subordinate clause precedes the main clause, like this:\\
\\
``When subjects were aware of the purpose of the experiment, no effect was
observed.''\\
\\
Furthermore:\\
\\
      ``We discarded specimens that had become contaminated.''\\
\\
In this case, the relative clause is restrictive because it deﬁnes exactly which specimens
were discarded. Restrictive clauses should not be preceded by a comma.\\
\\
  In contrast, a non-restrictive clause gives additional information about an object that
has already been identiﬁed; for example:\\
\\
      ``The ﬁle server uses the XFS ﬁle system, which supports journaling and pro-
      vides excellent performance.''\\
\\
In this case, the relative clause does not restrict or deﬁne the particular ﬁle system being
talked about, but merely provides additional information. Non-restrictive clauses should
be preceded by a comma.}}

### 2009-03-05 doc/ws-programming-tutorial/doc/tex_echoservice/echoservice.tex
Finished the Secure Echo Web Service and made first correction of the chapters.

The next service to be presented is the Echo Web Service.
Its task is to return the content of the received message back to the client.
Furthermore, the service provides two additional operations called ``ordinary'' and ``reverse''.
Depending on the operation chosen by the client, the message gets returned unmodified or reversed.
The goal of this chapter is to offer a deeper knowledge about message processing.
Also, the \textit{WSDL} (Web Services Description Language) will be introduced, with which the section now starts.

@@

Web Services can be specified (not implemented) by a meta language called \textit{WSDL} (Web Services Description Language).
Beside the description of the service, WSDL renders the possibility that services can be discovered by service brokers.
The discovery of services may be useful for an automatic adaption of a running client, i.e. if the endpoint of the service changes or to share the load of demands.
The WSDL service specification enables the programmer to implement a suitable client which interfaces the service in a proper way.
WSDL describes the structure of the messages, the intended use of the messages, the supported protocols and the endpoint of the service (URL).
\task{For that last reason, every instance of a service must be produced a distinct WSDL file for - or - it is automatically prepared from the information that the server has available once it is implemented. - ?MG }\\

The WSDL file that specifies the here presented Echo Web Service is shown in listing~\ref{lst:echo_wsdl}. 
It is composed of five main elements:
\newcommand{\parboxWidth}{13cm}
\begin{itemize}
	\item \textbf{Types} --- The element \textit{types} contains the description of the message structures and is written in the language XSD (XML Schema Definition). The data types used for the messages of the Echo Web Service are defined starting with the  line~\ref{lst_code:echo_wsdl_types}.

@@

	\item \textbf{Port type} --- The element \textit{portType} is used to assign the messages to an interface. Four interface types can be distinguished: One-way (input), request-response (input, output), solicit-response (input, output, fault) and notification (output).
	The echo service realises a solicit-response interface which is declared subsequent to line~\ref{lst_code:echo_wsdl_portType}. % in the lines followed by the line X

@@

\end{itemize}
%\textcolor{white}{newline}
\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:echo_wsdl,float=p,
	caption={[WSDL file describing the echo service. Filename: echo.wsdl]
	\textbf{WSDL file describing the echo service. Filename: echo.wsdl}}
	]
{../src/services/echoservice/echo.wsdl}
\task{Validate WSDL}

\subsection{The SOAP Fault Element}

The optional SOAP Fault element is used to indicate error messages in case of the port type \textit{solicit-response} (input, output, fault).
If a \textit{Fault} element is present, it must appear as a child element of the \textit{Body} element. A \textit{Fault} element can only appear once in a SOAP message.

The SOAP Fault element has the following sub elements:
\begin{tabular}{lp{9cm}}
Sub Element 	& Description \\
<faultcode> 	& A code for identifying the fault \\
<faultstring> 	& A human readable explanation of the fault \\
<faultactor> 	& Information about who caused the fault to happen \\
<detail> 	& Holds application specific error information related to the Body element\\
\end{tabular}

SOAP Fault Codes

The faultcode values defined below must be used in the faultcode element when describing faults:
\begin{tabular}{lp{9cm}}
Error           & Description \\
VersionMismatch & Found an invalid namespace for the SOAP Envelope element \\
MustUnderstand  & n immediate child element of the Header element, with the mustUnderstand attribute set to "1", was not understood \\
Client          & he message was incorrectly formed or contained incorrect information \\
Server          & here was a problem with the server so the message could not proceed \\
\end{tabular}

\task{Source of the above two tables? Extension of the second table? Numbers??}

More information about WSDL may be found at \href{http://www.w3.org/TR/wsdl}{http://www.w3.org/TR/wsdl}.

@@

This section presents the implementation of the service defined in the WSDL file of the previous section.
The source code of the C++ file is shown in listing~\ref{lst:echo_service_cpp}.
The header file will be set aside for it contains only redundant information. 
It can be reread in the source directory that is accompanying the tutorial.
Regarding to the source code of the Echo Web Service basically three changes of the Time Web Service source code will be required.
The first change concerns the constructor and can be found at line~\ref{lst_code:echo_cpp_prefix}.
Two strings are extracted of the server configuration file which later are used to envelope the message before it is returned.
Furthermore, a new method \textit{makeFault} in line~\ref{lst_code:echo_cpp_makeFault} has been introduced which is able to create the fault messages and is called by the method \textit{process}.
Within the method \textit{process} two new code fragments are now extracting and analyzing the incoming message, to be seen at line~\ref{lst_code:echo_cpp_extracting} and \ref{lst_code:echo_cpp_analyzing}.
In case something unexpected happens both will create a SOAP fault message.\\
% Vielleicht noch etwas über das extrahieren der Nachricht schreiben

\lstsetCPP
\lstinputlisting
	[
	label=lst:echo_service_cpp,
	caption={[C++ implementation of the echo service. Filename: echoservice.cpp]
	\textbf{C++ implementation of the echo service. Filename: echoservice.cpp}}
	]
{../src/services/echoservice/echoservice.cpp}

Again, the HED is configured by an XML file and is launched as introduced earlier.
The server configuration file is shown in Listing~\ref{lst:echo_hed_configuration_xml}.
The only change concerns the lines~\ref{lst_code:echo_hed_configuration_xml_pre} and \ref{lst_code:echo_hed_configuration_xml_pre} which specify the \textit{prefix} and \textit{suffix}.
The parameters will be extracted in the constructor of the service and explain nicely how settings can be passed from the server configuration file towards the service.

\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:echo_hed_configuration_xml, float=htb,
	caption={[Server configuration file for the echo service. Filename: arched\_echoservice.xml]
	\textbf{Server configuration file for the echo service. Filename: arched\_echoservice.xml}}
	]
{../src/services/echoservice/arched_echoservice.xml}

@@

With the interface of the server gaining complexity, so is the code for the client - for two reasons. Firstly, because the additional arguments need to be filled. Secondly, because of the extra effort to interact with the (here human) user to collect the data to forward to the Echo Web Service.
The parameters are now passed by the command line, to be seen in the lines followed by line~\ref{lst_code:echo_client_cpp_arguments}.
That code is independent from the ARC library.
The creation of the SOAP client is unchanged and the request is created in the lines subsequent line~\ref{lst_code:echo_client_cpp_request}.
It is processed in the code after line~\ref{lst_code:echo_client_cpp_response} in which also the response is received.
The checks of the response have expanded by an additional condition which tests for a fault message, see line~\ref{lst_code:echo_client_cpp_fault}.

\lstsetCPP
\lstinputlisting
	[
	label=lst:arcecho_arched_xml,
	caption={[HED configuration file for the ARC echo service. Filename: arcecho\_no\_ssl.xml]
	\textbf{HED configuration file for the ARC echo service. Filename: arcecho\_no\_ssl.xml\textcolor{white}{hmf}}}
	]
{../src/clients/echoclient/echoclient.cpp}

@@

\lstsetKSH
\begin{lstlisting}[
label=lst:invokation_echoservice, float=!htb,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
$ ./echoclient http://localhost:60000/echo ordinary text_to_be_transmitted
[ text_to_be_transmitted ]
$ ./echoclient http://localhost:60000/echo reverse text_to_be_transmitted
[ dettimsnart_eb_ot_txet ]
$ ./echoclient http://localhost:60000/echo re2verse text_to_be_transmitted
A SOAP fault occured:
  Fault code:   4
  Fault string: "Unknown operation. Please use "ordinary" or "reverse""
\end{lstlisting}

A few examples of exchanged messages are shown in the Listings~\ref{lst:echoservice_request}, \ref{lst:echoservice_response} and \ref{lst:echoservice_fault}. Listing~\ref{lst:echoservice_request} illustrates a request message using the operation \textit{reverse}.
Listing~\ref{lst:echoservice_response} illustrates the corresponding response message. When the operation requested by the client is unknown, then the server replies with the fault message shown in Listing~\ref{lst:echoservice_fault}.

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:echoservice_request, float=!htb,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <echo:echoRequest>
      <echo:say operation="reverse">text_to_be_transmitted</echo:say>
    </echo:echoRequest>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:echoservice_response, float=!htb,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <echo:echoResponse>
      <echo:hear>[ dettimsnart_eb_ot_txet ]</echo:hear>
    </echo:echoResponse>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:echoservice_fault, float=!htb,
caption={[Transformation in eine uniforme konzentrische Verteilung.]
         \textbf{Transformation in eine uniforme konzentrische Verteilung.\textcolor{white}{hmf}}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <soap-env:Fault>
      <soap-env:faultcode>soap-env:Client</soap-env:faultcode>
      <soap-env:faultstring>Unknown operation. Please use "ordinary" or "reverse"</soap-env:faultstring>
    </soap-env:Fault>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}

>>>>

The next service presented is the Echo Web Service.
Its task is to return the content of the received message back to the client.
Furthermore, the service provides two additional operations called ``ordinary'' and ``reverse''.
Depending on the operation chosen by the client, the message gets returned unmodified or reversed.
The goal of this chapter is to offer a deeper knowledge about message processing.
Also, the \textit{WSDL} (Web Services Description Language) will be introduced, with which the section now starts.

@@

Web Services can be specified (not implemented) by a meta language called \textit{WSDL} (Web Services Description Language).
Beside the description of the service, WSDL renders the possibility that services can be discovered by service brokers.
The discovery of services may be useful for an automatic adaption of a running client, i.e. if the endpoint of the service changes or to share the load of demands.
The WSDL service specification enables a foreign programmer to implement a suitable client which interfaces the service in a proper way.
WSDL describes the structure of the messages, the intended use of the messages, the supported protocols and the endpoint of the service (URL).
\task{For that last reason, every instance of a service must be produced a distinct WSDL file for - or - it is automatically prepared from the information that the server has available once it is implemented. - ??MG }\\

The WSDL file that specifies the here presented Echo Web Service is shown in Listing~\ref{lst:echo_wsdl}. 
It is composed of five main elements:
\newcommand{\parboxWidth}{13cm}
\begin{itemize}
	\item \textbf{Types} --- The element \textit{types} contains the description of the message structures and is written in the language XSD (XML Schema Definition). The data types used for the messages of the Echo Web Service are defined starting with the  line~\ref{lst_code:echo_wsdl_types}.

@@

	\item \textbf{Port type} --- The element \textit{portType} is used to assign the messages to an interface. Four interface types can be distinguished: One-way (input), request-response (input, output), solicit-response (input, output, fault) and notification (output).
	The Echo Web Service realises a solicit-response interface which is declared subsequent to line~\ref{lst_code:echo_wsdl_portType}. % in the lines followed by the line X

@@

\end{itemize}
%\textcolor{white}{newline}
\lstsetJUSTXML
\lstinputlisting
	[
	label=lst:echo_wsdl,
	caption={[WSDL file describing the echo service. Filename: echo.wsdl]
	\textbf{WSDL file describing the echo service. Filename: echo.wsdl}}
	]
{../src/services/echoservice/echo.wsdl}
\task{TODO: Validate the WSDL Listing}

\subsection{The SOAP Fault Message}

A SOAP fault message is always located within the body element and can appear only one time. 
It indicates error messages in case the port type \textit{solicit-response} (input, output, fault) has been chosen.
An element called \textit{fault} encapsulates diffrent types of elements which are describing the fault.
These elements are listed in Table~\ref{tbl:fault_elements}.
\begin{table}[h]
 \centering
 \caption{Elements of the fault message.}
 \label{tbl:fault_elements}
	\begin{tabular*}{\textwidth}[t]{p{2cm}p{13cm}}
	\hline
	\textbf{Element}        & \textbf{Description}\\
	\hline
	\textbf{faultcode} 	& Code which shall identify the fault.\\
	\textbf{faultstring} 	& A human readable explanation of the fault.\\
	\textbf{faultactor} 	& Information about who caused the fault to happen.\\
	\textbf{detail}         & Holds application specific error information.\\
	\hline\\
	\end{tabular*}
\end{table}
The fault code describes the generic class of the fault. The ARC implementation assigns each fault a certain number.
The fault code along with its description is described within the Table~\ref{tbl:faultcode}
\begin{table}[h]
 \centering
 \caption{Possible fault codes.}
 \label{tbl:faultcode}
	\begin{tabular*}{\textwidth}[t]{p{2cm}p{4cm}p{9cm}}
	\hline
	\textbf{Fault code} & \textbf{Error} & \textbf{Description}\\
	\hline
	0 & \textbf{undefined}       & --- \\
	1 & \textbf{unknown}         & Reason for failure couldn't be identified.\\
	2 & \textbf{VersionMismatch} & Found an invalid namespace for the SOAP Envelope element.\\
	3 & \textbf{MustUnderstand}  & The processing of the SOAP header is optional unless the flag mustUnderstand is set ``true''. If, according to that case, the SOAP service is not able to understand the header a fault message with the faultcode MustUnderstand is returned. \\
	4 & \textbf{Client}          & The request message was incorrectly formed or contained incorrect information.\\
	5 & \textbf{Server}          & There was a problem with the server so the message could not proceed \\
	6 & \textbf{DataEncodingUnknown} & The message couldn't be processed due to encoding problems\\
	\hline
	\end{tabular*}
\end{table}

For morde information about WSDL it is recommended to check the internet address~\href{http://www.w3.org/TR/wsdl}{http://www.w3.org/TR/wsdl}.

@@

This section presents the implementation of the service defined in the WSDL file of the previous section.
The source code is shown in Listing~\ref{lst:echo_service_cpp}.
The header file will be set aside for it contains only redundant information. 
It can be reread in the source directory that is accompanying the tutorial.
Regarding to the source code of the Echo Web Service basically three changes of the Time Web Service source code are required.
The first change concerns the constructor and can be found at line~\ref{lst_code:echo_cpp_prefix}.
Two strings are extracted of the server configuration file which are later used to envelope the message before it is returned.
Furthermore, a new method \textit{makeFault} in line~\ref{lst_code:echo_cpp_makeFault} has been introduced which is able to create a fault messages.
Within the method \textit{process} two new code fragments are now extracting and analyzing the incoming message, to be seen at line~\ref{lst_code:echo_cpp_extracting} and \ref{lst_code:echo_cpp_analyzing}.
In case something unexpected happens both will create a SOAP fault message.\\
% Vielleicht noch etwas über das extrahieren der Nachricht schreiben

\lstsetCPP
\lstinputlisting
	[
	label=lst:echo_service_cpp,
	caption={[Implementation of the Echo Web Service.]
	\textbf{Implementation of the Echo Web Service.}}
	]
{../src/services/echoservice/echoservice.cpp}

Again, the HED is configured by an XML file and launched in the same manner as introduced before.
The server configuration file is shown in Listing~\ref{lst:echo_hed_configuration_xml}.
The only change concerns the lines~\ref{lst_code:echo_hed_configuration_xml_pre} and \ref{lst_code:echo_hed_configuration_xml_pre} which specify the \textit{prefix} and \textit{suffix}.
The parameters will be extracted in the constructor of the service and explain nicely how settings can be passed from the server configuration file towards the service.

\lstsetARCHEDXML
\lstinputlisting
	[
	label=lst:echo_hed_configuration_xml, float=htb,
	caption={[Server configuration file of the Echo Web Service]
	\textbf{Server configuration file of the Echo Web Service}}
	]
{../src/services/echoservice/arched_echoservice.xml}

@@

With the interface of the server gaining complexity, so is the code for the client - for two reasons. Firstly, because the additional arguments need to be filled. Secondly, because of the extra effort to interact with the (here human) user to collect the data which needs to be forwarded to the Echo Web Service. The source code of the client is shown Listing~\ref{lst:client_echo_cpp}.
The parameters are now passed by the command line, to be seen in the lines followed by line~\ref{lst_code:echo_client_cpp_arguments}.
That code is independent from the ARC library.
The creation of the SOAP client is unchanged and the request is created in the lines subsequent to line~\ref{lst_code:echo_client_cpp_request}.
It is processed in the code after line~\ref{lst_code:echo_client_cpp_response} in which is also the response is received.
The checks of the response have expanded by an additional condition which tests for a fault message, see line~\ref{lst_code:echo_client_cpp_fault}.

\lstsetCPP
\lstinputlisting
	[
	label=lst:client_echo_cpp,
	caption={[Implementation of the client program.]
	\textbf{Implementation of the client program.}}
	]
{../src/clients/echoclient/echoclient.cpp}

@@

\lstsetKSH
\begin{lstlisting}[
label=lst:invokation_echoservice, float=!htb,
caption={[Three diffrent invokations of the client program.]
         \textbf{Three diffrent invokations of the client program.}}]
$ ./echoclient http://localhost:60000/echo ordinary text_to_be_transmitted
[ text_to_be_transmitted ]
$ ./echoclient http://localhost:60000/echo reverse text_to_be_transmitted
[ dettimsnart_eb_ot_txet ]
$ ./echoclient http://localhost:60000/echo re2verse text_to_be_transmitted
A SOAP fault occured:
  Fault code:   4
  Fault string: "Unknown operation. Please use "ordinary" or "reverse""
\end{lstlisting}

A few examples of exchanged messages are shown in the Listings~\ref{lst:echoservice_request}, \ref{lst:echoservice_response} and \ref{lst:echoservice_fault}. Listing~\ref{lst:echoservice_request} illustrates a request message using the operation \textit{reverse} while Listing~\ref{lst:echoservice_response} illustrates the corresponding response message.
The last Listing~\ref{lst:echoservice_fault} shows the fault message which is created by the service after the client requested an unknown operation.

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:echoservice_request, float=!htb,
caption={[Request message created by the client.]
         \textbf{Request message created by the client.}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <echo:echoRequest>
      <echo:say operation="reverse">text_to_be_transmitted</echo:say>
    </echo:echoRequest>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:echoservice_response, float=!htb,
caption={[Response message created by the service.]
         \textbf{Response message created by the service.}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <echo:echoResponse>
      <echo:hear>[ dettimsnart_eb_ot_txet ]</echo:hear>
    </echo:echoResponse>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}

\lstsetJUSTXML
\begin{lstlisting}[
label=lst:echoservice_fault, float=!htb,
caption={[Fault message created by the service..]
         \textbf{Fault message created by the service.}}]
<soap-env:Envelope xmlns:echo="urn:echo" xmlns:soap-enc="http://schemas.xmlsoap.org/soap/encoding/" xmlns:soap-env="http://schemas.xmlsoap.org/soap/envelope/" xmlns:xsd="http://www.w3.org/2001/XMLSchema" xmlns:xsi="http://www.w3.org/2001/XMLSchema-instance">
  <soap-env:Body>
    <soap-env:Fault>
      <soap-env:faultcode>soap-env:Client</soap-env:faultcode>
      <soap-env:faultstring>Unknown operation. Please use "ordinary" or "reverse"</soap-env:faultstring>
    </soap-env:Fault>
  </soap-env:Body>
</soap-env:Envelope>
\end{lstlisting}
